Cell-type diversity and connectome of the ctenophore apical organ

### 2024-03-10 manuscript/Manuscript.qmd
Ms: add ref

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

@@

The easiest way is to use the command line:

@@

"synaptic regions with the characteristic presynaptic triad mor-
phology of ctenophore nerves (i.e., a single layer of
vesicles, smooth ER sac, and closely apposed mito-
chondria; Horridge and Mackay, 1964; Hernandez-
Nicaise, 1973)"

>>>>

@@

The easiest way is to use the command line to add new refs to the .bib file:

@@

"synaptic regions with the characteristic presynaptic triad mor-
phology of ctenophore nerves (i.e., a single layer of
vesicles, smooth ER sac, and closely apposed mito-
chondria [@Horridge_1964; @Hernandez_Nicaise_1973] Hernandez-
Nicaise, 1973)"
